Multi-task learning in Computer Vision

### 2020-03-30 5-Multitask.tex
checkpoint

Once the loss function is specified, the actual training is quite similar to training a Single-task model.
The one new thing to consider in a Multi-task setting is the sampling ratio of the different tasks as some tasks can be easier to learn or contain significantly more or less data compared to other tasks.

>>>>

Once the loss function is specified, the actual training is quite similar to training a Single-task model.
The one new thing to consider in a Multi-task setting is the sampling ratio of the different tasks as some tasks can be easier to learn or contain significantly more or less data compared to other tasks.
Like in normal training, the models are trained one batch at a time.
In a Multi-task setting, we have datasets for each of the tasks from which we can pick at a time.
Now, we can define an epoch in the training process as several batches with an expected value of $\sum_i{ \dfrac{|X_i| \alpha_i}{B_i}}$ batches over $i$ tasks, where $|X_i|$ is the training size, $B_i$ is the batch size, and $\alpha_i$ is the scaling factor for each task.
Iterating through all batches can be done in a round-robin fashion,  going through all batches of each data set at a time or randomly sampling the sets with probabilities respective to their magnitude and scaling factor.
